---
title: "[Your Report Title]"
author: "[Your Name]"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 0. Setup

```{r libraries}
# load libraries
library(data.table)
library(tidyverse)
library(here)

# Other settings
COL_TIMS <- "#003F5C"
COL_CCRS <- "#FF6361"
```

---

## 1. [Section Title]

Write 1-2 sentences explaining what this section does and why.

```{r section-1}
# Comment on WHY, not WHAT
# E.g.: restrict to post-policy period (AB 413 effective Jan 2024)
```

---

## 2. [Section Title]

```{r section-2}

```

---

## 3. Results

Describe what the table or figure shows before displaying it.\n

e.g. point estimates & 95% CI vs. bandwidth (triangular kernel)
```{r results-plot, fig.width=9, fig.height=5}
# Always set fig.width and fig.height in chunk options
# ggsave()
# saveRDS()
# write.csv()

```

---

## Summary

Write 2-3 sentences summarizing the key takeaway.\n

e.g. Under a triangular kernel, increasing the bandwidth beyond 10-12 months 
does not improve the precision of the estimates.